\documentclass[char]{AtlanticCity}
\begin{document}
\name{\cBond{}}

You are the best of the best. When the mission is impossible, headquarters calls you. And that's what you are doing in Monte-Carlo tonight. You've been on the trail of a bizarre anomaly recently - a spy. A new spy. And a good one at that. Out of no where. Your job is to find them and neutralize them before they can compromise your contacts in the city. To make matters worse, new evidence out of Venice suggests that a particularly high profile art thief is in Monaco somewhere. Headquarters saw fit to task you with that as well. As if you don't have enough to do already.

It's times like this that you wish your partner, \cPartner{} was still around. Still, you suppose it is for that reason that it is against regulation to get sexually involved with your partner. Of course you remember the night you lost them like it was yesterday. The five years have done nothing to dull the sights and smells that haunt you to this day.

It was summer in Morocco. You and \cPartner{} were hot on the trail of a terrorist cell. You'd stopped for the night in a small bed and breakfast. In the middle of the night, you both woke to screaming coming from downstairs. \cPartner{\They} was always a touch quicker to wake up than you. \cPartner{} had jumped out of bed like it was scalding, and whipped out a length of rope. \cPartner{\They} had you tied to a chair before you could parse enough of what was happening to fight back. Then \cPartner{\They} took \cPartner{\their} gun and went downstairs. You heard shots fired. More shots than \cPartner{}'s gun had. By the time you slipped your bonds and got downstairs, everyone was gone. There was blood everywhere, bullet holes riddled the walls in several places, and \cPartner{} was no where to be found. You wanted to pursue, make the terrorists pay, but headquarters recalled you immediately. They had already lost one top agent, they weren't willing to risk a second.

Lingering in the past won't solve today's problems though. Through great effort, you have secured evidence (scant though it may be) that the mysterious new spy may be trying to turn the dealer at the high stakes table in the Hotel de Monte-Carlo into a double agent. If you can catch them in the act, you wouldn't even need to get approval from headquarters to neutralize them  later tonight. In a skin crawling \emph{coincidence}, it seems that the art thief may frequent the very same hotel. You've been a spy for too long to believe in coincidence. The situation is perilous, and you are wholly without backup tonight. But you are the one headquarters sent for a reason. If anyone can survive this and come out of it with crucial information, it's you.


\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	%\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
